---
title: "p8105_hw3_jt3098"
author: "Jieqi Tu (jt3098)"
date: "10/5/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```


## Problem 1
```{r Importing data}
# Importing data from guthub website
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
data(brfss_smart2010, package = "p8105.datasets")
```

```{r Data manipulation}
brfss_smart2010 = 
  brfss_smart2010 %>%
  janitor::clean_names() %>% # Change upper-case letter to lower-case letter
  filter(topic == "Overall Health") # Focus on the topic of Overall Health
```

## Problem 2
```{r Importing data for problem 2}
data("instacart", package = "p8105.datasets")
```

```{r intstacart questions}
# Calculate the number of aisles
n_aisle = 
  instacart %>%
  distinct(aisle) %>%
  nrow()

# Count the most ordered aisle
count_(instacart, 'aisle', sort = TRUE)
```

About this dataset:

* This instacart dataset has 15 variables in total. It includes user ID, product ID, order number, order hour of day, days since prior order, etc.
* The mean of order hour of day is `r mean(instacart$order_hour_of_day, rm.na = TRUE)`, and the standard deviation of order hour of day is `r sd(instacart$order_hour_of_day)`.
* The mean of days since prior order is `r mean(instacart$days_since_prior_order, rm.na = TRUE)`, and the standard deviation of days since prior order is `r sd(instacart$days_since_prior_order)`.
* The number of aisle is `r n_aisle`, and the aisle that most items ordered from is fresh vegetables with 150609 orders.

```{r plots of number of items ordered in each aisle}
instacart %>%
  group_by(aisle) %>%
  summarise(total_aisle = n()) %>%
  ggplot(aes(x = aisle, y = total_aisle)) +
  geom_point() +
  labs(
    x = "Aisle Names",
    y = "Number of Items Ordered",
    title = "Number of Items Ordered in Each Aisle"
  ) +
  theme_bw()
```

